DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-06-30 ase2017/paper.tex
fixed typo
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

In Fig.~\ref{toolbox-usage}, ``num'' represents $A(z)$ and ``den'' represent $B(z)$, while 
$y$ represents the synthesized stable digital controller, which is defined by Eq.(\ref{equation_controller}).
%
\begin{equation}
\label{equation_controller}
C(z)=\frac{-0.9983^{2}+0.09587z+0.1926}{z^2+0.5665z+0.75}.
\end{equation}

>>>>

In Fig.~\ref{toolbox-usage}, ``num'' represents $B(z)$ and ``den'' represent $A(z)$, while 
$y$ represents the synthesized stable digital controller, which is defined by Eq.(\ref{equation_controller}).
%
\begin{equation}
\label{equation_controller}
C(z)=\frac{-0.9983^{2}+0.09587z+0.1926}{z^2+0.5665z+0.75}.
\end{equation}
